STAT 133 Final Project: Visualizing Berkeley Police Data

### 2016-08-10 final_paper/STAT 133 Final Project_ Visualizing Berkeley Police Data.Rmd
final paper

---
title: "STAT 133 Final Project: Visualizing Berkeley Police Data"
author: "Amy Zhu, Mengyu Li, Rebecca Reus, and Shangjun Jiang"
date: "9 August 2016"
output: 
    pdf_document:
    latex_engine: xelatex
sansfont: Times New Roman

@@

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sp)
library(ggmap)
library(tidyr)
library(readr)
library(plyr)
library(dplyr)
library(ggvis)
library(tidyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(readr)
library(data.table)
library(maps)
library(mapdata)
library(maptools)
library(scales)
library(RgoogleMaps)
library(rgdal)
library(rgeos)
library(RColorBrewer)
library(grid)
library(gridExtra)
library(pander)
library(formattable)
library(pander)
library(extrafont)
setwd("~/Desktop/Stats R/PROJECT/FINALPAPER/finalproject_angry_ladies/final_paper")
```

@@

```{r, warning = FALSE, echo = F, fig.width = 8, fig.height = 3, message = FALSE, fig.align="center", fig.cap= "Berkeley Police Stops"}
map_stop1 # figure 5
```

@@

```{r, warning = FALSE, echo = F, fig.width = 8, fig.height = 3, message = FALSE, fig.align="center", fig.cap= "2015-2016 Police Stop Density (left) and 2010 Census Tract Population Density (right)"}
grid.arrange(stopdensitymap4, popdenmap, ncol=2) # figure 6
```

@@

```{r, fig.height = 3, fig.width = 10, echo=FALSE, warning = FALSE, message = FALSE, fig.align="center", fig.cap= "Police Stop Density Map by Race"}
stopdensitymap3 # figure 7
```

@@

```{r, warning = FALSE, echo = FALSE,  fig.width = 15, fig.height = 3, message = FALSE, fig.align = "center", fig.cap= "Berkeley Population Density Map by Race"}
grid.arrange(a2,black2,h2,o2,w2, ncol = 5) # print population density by race # figure 8
```

@@

```{r, message = F, echo = FALSE, fig.width = 10, fig.height = 3, warning = FALSE, fig.align="center", fig.cap= "Police Stops in Berkeley by Race"}
grid.arrange(bargraph1, bargraph2, ncol = 2)
```

@@

```{r, echo=FALSE, warning=F,message=F, fig.align="center", fig.width = 10, fig.height=7, fig.cap = "Police Stops Leading to Arrests"}
grid.arrange(map_arrested1, map_enforcement, ncol=1)
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Police Stops by Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
map_reasons1
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Conditional Probability of Being Arrested During a Police Stop: Race VS Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_arrest # figure 12
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Conditional Probability of Being Arrested During a Police Stop: Age VS Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_arrest_age # figure 13
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Conditional Probability of Being Arrested During a Police Stop: Gender VS Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_arrest_gender # figure 14
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Conditional Probability of Being Arrested During a Police Stop: Race VS Hour", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_percentage3 # figure 15
```
Figure 16 implies that people aged from 18 to 29 are more liable to be stopped by police in Berkeley at night. The average ratio of people aged from 18 to 29 to all people stopped by the Berkeley Police Department at night is greater than 40%. The figure also implies that people aged 40+ are more liable to be stopped by the police during the daytime. The average ratio of people aged 40+ to all people stopped by police during the day is greater than 40%. Further, the ratio of stops of people aged 0-18 and people aged 30-39 fluctuates during the daytime and the night, with an average ratio of 2.5% and 25% respectively.

```{r, fig.height = 3, fig.width = 10, fig.cap= "Conditional Probability of Arrested  During a Police Stop: Age VS Hour", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
stop_percentage2 # figure 16
```

@@

```{r, echo=FALSE, fig.cap= "Arrested and Jailed in Berkeley", warning = FALSE, message=FALSE, fig.height = 3, fig.width = 10, fig.align="center"}
grid.arrange(bararrest, barjail, ncol = 2) # figure 17
```

>>>>

---
title: "STAT 133 Final Project: Visualizing Berkeley Police Data"
author: "Amy Zhu, Mengyu Li, Rebecca Reus, and Shangjun Jiang"
date: "9 August 2016"
output: 
    pdf_document:
    latex_engine: xelatex
    fig_caption: yes
    keep_tex: yes
header-includes: \usepackage{float}
sansfont: Times New Roman

@@

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE, cache = TRUE, fig.pos = 'H')
library(sp)
library(ggmap)
library(tidyr)
library(readr)
library(plyr)
library(dplyr)
library(ggvis)
library(tidyr)
library(stringr)
library(lubridate)
library(ggplot2)
library(readr)
library(data.table)
library(maps)
library(mapdata)
library(maptools)
library(scales)
library(RgoogleMaps)
library(rgdal)
library(rgeos)
library(RColorBrewer)
library(grid)
library(gridExtra)
library(pander)
library(formattable)
library(pander)
library(extrafont)
setwd("~/Desktop/Stats R/PROJECT/FINALPAPER/finalproject_angry_ladies/final_paper")

@@

```{r, warning = FALSE, echo = F, fig.width = 8, fig.height = 3, message = FALSE, fig.align="center", fig.cap= "Berkeley Police Stops", fig.show="asis"}
map_stop1 # figure 5
```

@@

```{r, warning = FALSE, echo = F, fig.width = 8, fig.height = 2, message = FALSE, fig.align="center", fig.cap= "2015-2016 Police Stop Density (left) and 2010 Census Tract Population Density (right)", fig.show="asis"}
grid.arrange(stopdensitymap4, popdenmap, ncol=2) # figure 6
```

@@

```{r, fig.height = 2, fig.width = 10, echo=FALSE, warning = FALSE, message = FALSE, fig.align="center", fig.cap= "Police Stop Density Map by Race", fig.show="asis"}
stopdensitymap3 # figure 7
```

@@

```{r, warning = FALSE, echo = FALSE,  fig.width = 15, fig.height = 3, message = FALSE, fig.align = "center", fig.cap= "Berkeley Population Density Map by Race", fig.show="asis"}
grid.arrange(a2,black2,h2,o2,w2, ncol = 5) # print population density by race # figure 8
```

@@

```{r, message = F, echo = FALSE, fig.width = 10, fig.height = 3, warning = FALSE, fig.align="center", fig.cap= "Police Stops in Berkeley by Race", fig.show="asis"}
grid.arrange(bargraph1, bargraph2, ncol = 2)
```

@@

```{r, echo=FALSE, warning=F,message=F, fig.align="center", fig.width = 10, fig.height=5, fig.cap = "Police Stops Leading to Arrests", fig.show="asis"}
grid.arrange(map_arrested1, map_enforcement, ncol=1)
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Police Stops by Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center", fig.show="asis"}
map_reasons1
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Conditional Probability of Being Arrested During a Police Stop: Race VS Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center", fig.show="asis"}
stop_arrest # figure 12
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Conditional Probability of Being Arrested During a Police Stop: Age VS Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center", fig.show="asis"}
stop_arrest_age # figure 13
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Conditional Probability of Being Arrested During a Police Stop: Gender VS Reason", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center", fig.show="asis"}
stop_arrest_gender # figure 14
```

@@

```{r, fig.height = 3, fig.width = 10, fig.cap= "Conditional Probability of Being Arrested During a Police Stop: Race VS Hour", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center", fig.show="asis"}
stop_percentage3 # figure 15
```
Figure 16 implies that people aged from 18 to 29 are more liable to be stopped by police in Berkeley at night. The average ratio of people aged from 18 to 29 to all people stopped by the Berkeley Police Department at night is greater than 40%. The figure also implies that people aged 40+ are more liable to be stopped by the police during the daytime. The average ratio of people aged 40+ to all people stopped by police during the day is greater than 40%. Further, the ratio of stops of people aged 0-18 and people aged 30-39 fluctuates during the daytime and the night, with an average ratio of 2.5% and 25% respectively.

```{r, fig.height = 3, fig.width = 10, fig.cap= "Conditional Probability of Arrested  During a Police Stop: Age VS Hour", echo=FALSE, warning = FALSE, message = FALSE, fig.align = "center", fig.show="asis"}
stop_percentage2 # figure 16
```

@@

```{r, echo=FALSE, fig.cap= "Arrested and Jailed in Berkeley", warning = FALSE, message=FALSE, fig.height = 3, fig.width = 10, fig.align="center", fig.show="asis"}
grid.arrange(bararrest, barjail, ncol = 2) # figure 17
```
